%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Md. Shahibur Rahman} % Your name
\address{Palashi, Dhaka-1205, Bangladesh} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+880)1617405074 \\ 1505074.msr@ugrad.cse.buet.ac.bd} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bangladesh University of Engineering and Technology} \hfill {\em February 2016 - Present} 
\\ Bachelor of Science(BSc) in Computer Science and Engineering(CSE)
\\ Department of Computer Science and Engineering\\
\\{\bf Notre Dame College, Dhaka} \hfill {\em July 2013 - June 2015} 
\\ Higher Secondary Education in Science
\\{\bf Maheshpur Govt. High School, Maheshpur Jhenidah}\hfill {\em January 2008-March 2013 }
\\ Secondary Education
\\{ \bf Al-Helal Institute Kindergarten } \hfill{ \em January 2003-December 2007}
\\ Primary Education
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Online Market Place}
\\In our current semester, we, a group of three students have built a website which can manage huge existing market online. This website has three module, one is admin module, one is shopowner module and one is customer module. Each type of users can find benefit from our project
\\ We've built this project using laravel framework with MySQL database in back-end, and html, css and bootstrap in front-end.\\
\\{\bf School Management}\\
 In my fourth semester of my university life I made a software for school management. All documents and records of a school can be stored to this and anyone(student and teacher or guardian ) can use this to know more information easily. 
 \\ I made this using JavaFx and Oracle database.


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & C, C++, JAVA, PYTHON, PHP, Matlab, ShellScript \\
Databases \ & Oracle, MySQL\\
Framework \ & Laravel\\
Software \& Tools & Latex \\
Algorithm and Data Structure\\ 
Debugging \ & I am good at debugging code
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{}{}{}{}
\item I am still a student. I have no work experience yet.
\end{rSubsection}


\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} 
\begin{enumerate}
    \item {Second Runner up in Junior Category at Divisional Mathematical Olympiad, Kustia, 2009}
\item Champion in Junior Category at Divisional Mathematical Olympiad, Jessore, 2011
\item First Runner up in Junior Category at National Mathematical Olympiad, Dhaka, 2011
\item Champion in Secondary Category at Divisional Mathematical Olympiad, Jessore, 2012
\item First Runner up in Secondary Category at National Mathematical Olympiad, Dhaka, 2012
\item Selected for $8^{th}$ National Math Camp(2012) from where team national is formed for International Mathematical Olympiad, and participated
\item First Runner up in Secondary at Divisional Mathematical Olympiad, Jessore, 2013
\item Second Runner up in Secondary at Divisional Mathematical Olympiad, Dhaka, 2014
\item First Runner up in Secondary at National Mathematical Olympiad, Dhaka, 2014
\item Selected for $10^{th}$ National Math Camp(2014) from where national team is formed for International Mathematical Olympiad, and participated 
\end{enumerate}
\end{rSection}



%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
 I have solved about 150 problems in different online Judges. And I regularly participate in different programming contests.
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\begin{rSection}{Personal Traits}
\item Have strong Mathematical Back-Ground
\item Highly motivated and eager to learn new things.
\item Ability to work as an individual as well as in group.
\end{rSection}
\end{document}
